### 2019-03-24 results.tex
Updates from Overleaf

                        \hline
            BR
            & .271 & .484 & .486 & .802 &.292 & .572 & .529 & .654 & .0230 & .685 \\
            BR-support
            & .247 & .516 & .486 & .805 &.296 & .594 & .545 & .689 & \textbf{.0228} & .696\\
            PCC 
            & .279 & .480 & .595 & .818 &- & - & .541 & .688 & .0255 & .682 \\
            seq2seq-RNN  
             & .270 & .528 & .561 & .824 &.331 & .603 & .510 & .708 & .0254 & .701 \\
            Vinyals-RNN-uniform 
             & .279 & .527 & .578 & .826 & .313 & .567  & .532 & .721 & .0241 & .711\\
            Vinyals-RNN-sample
            & .300 & .531 & .590 & .828 & .339 & .597 &-&-&-&-\\
            Vinyals-RNN-max
            & .293 & .530 & .588 & .829 & .343 & .599 & .535 & .709 & .0256 & .700 \\
            Vinyals-RNN-max-direct
             & .226 & .518 & .539 & .808 & .313 & .583 &-&-&-&-\\
            SGM
            &-&-&-&-&-&-& - & - & .0245 & .710 \\
            set-RNN 
             & \textbf{.310} & \textbf{.538} & \textbf{.607} & \textbf{.838}  &\textbf{.361} & \textbf{.607} & \textbf{.548} & \textbf{.731} & .0241 & \textbf{.720}\\
            \hline

@@

                        \hline
            seq2seq-RNN  
             & .270$\to$.269 & .528$\to$.528& .561$\to$.561 & .824$\to$.824 &.331$\to$.336& .603$\to$.603 & .510$\to$.511 &.708$\to$.709 \\
            Vinyals-RNN-uniform  
             & .279$\to$.288& \textbf{.527}$\to$\textbf{.537}& .578$\to$.587& .826$\to$.833& \textbf{.313}$\to$\textbf{.336}& \textbf{.567}$\to$\textbf{.585} & \textbf{.532}$\to$\textbf{.542} &.721$\to$.724 \\
             Vinyals-RNN-sample
            & .300$\to$.303 & .531$\to$.537 &.590$\to$.597 & .828$\to$.833 & \textbf{.339}$\to$\textbf{.351} & .597$\to$.602 & - &- \\
            Vinyals-RNN-max
            & .293$\to$.301 & .530$\to$.535 & .588$\to$.585 & .829$\to$.830 & .343$\to$.352 &.599$\to$.604 & .535$\to$.537 &.709$\to$.712  \\
            Vinyals-RNN-max-direct
             & .226$\to$.228& .518$\to$.519& .539$\to$.538& .808$\to$.808& .313$\to$.316&.583$\to$.584 & - &- \\

>>>>

                        \hline
            BR
            & .271 & .484 & .486 & .802 &.292 & .572 & .529 & .654 & .0230 & .685 \\
            BR-support
            & .247 & .516 & .486 & .805 &.296 & .594 & .545 & .689 & \textbf{.0228} & .696\\
            PCC 
            & .279 & .480 & .595 & .818 &- & - & .541 & .688 & .0255 & .682 \\
            seq2seq-RNN  
             & .270 & .528 & .561 & .824 &.331 & .603 & .510 & .708 & .0254 & .701 \\
            Vinyals-RNN-uniform 
             & .279 & .527 & .578 & .826 & .313 & .567  & .532 & .721 & .0241 & .711\\
            Vinyals-RNN-sample
            & .300 & .531 & .590 & .828 & .339 & .597 & .527 & .706 & .0259 & .697 \\
            Vinyals-RNN-max
            & .293 & .530 & .588 & .829 & .343 & .599 & .535 & .709 & .0256 & .700 \\
            Vinyals-RNN-max-direct
             & .226 & .518 & .539 & .808 & .313 & .583 & .490 & .702 & .0257 & .694\\
            SGM
            &-&-&-&-&-&-& - & - & .0245 & .710 \\
            set-RNN 
             & \textbf{.310} & \textbf{.538} & \textbf{.607} & \textbf{.838}  &\textbf{.361} & \textbf{.607} & \textbf{.548} & \textbf{.731} & .0241 & \textbf{.720}\\
            \hline

@@

                        \hline
            seq2seq-RNN  
             & .270$\to$.269 & .528$\to$.528& .561$\to$.561 & .824$\to$.824 &.331$\to$.336& .603$\to$.603 & .510$\to$.511 &.708$\to$.709 \\
            Vinyals-RNN-uniform  
             & .279$\to$.288& \textbf{.527}$\to$\textbf{.537}& .578$\to$.587& .826$\to$.833& \textbf{.313}$\to$\textbf{.336}& \textbf{.567}$\to$\textbf{.585} & \textbf{.532}$\to$\textbf{.542} &.721$\to$.724 \\
             Vinyals-RNN-sample
            & .300$\to$.303 & .531$\to$.537 &.590$\to$.597 & .828$\to$.833 & \textbf{.339}$\to$\textbf{.351} & .597$\to$.602 & .527$\to$.530 & .706$\to$.708 \\
            Vinyals-RNN-max
            & .293$\to$.301 & .530$\to$.535 & .588$\to$.585 & .829$\to$.830 & .343$\to$.352 &.599$\to$.604 & .535$\to$.537 &.709$\to$.712  \\
            Vinyals-RNN-max-direct
             & .226$\to$.228& .518$\to$.519& .539$\to$.538& .808$\to$.808& .313$\to$.316&.583$\to$.584 & .490$\to$.490 &.702$\to$.701 \\
